\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{balance}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{}

% ISBN
\acmISBN{}

%Conference
\acmConference[PCSC2020]{Philippine Computing Science Congress}{March 2020}{City of Manila, Philippines}
\acmYear{2020}
\copyrightyear{2020}


\acmArticle{}
\acmPrice{}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
\editor{}
\editor{}
\editor{}


\begin{document}
\title{ASSYSTX: Supporting Collaboration in Course Loading Systems}
%\titlenote{Produces the permission block, and
  %copyright information}
%\subtitle{Subtitle}
%\subtitlenote{The full version of the author's guide is available as
  %\texttt{acmart.pdf} document}


\author{redacted}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{redacted}
  %\streetaddress{P.O. Box 1212}
  \city{Manila, Philippines}
  %\state{Ohio}
  %\postcode{43017-6221}
}
\email{redacted}

\author{redacted}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{redacted}
  %\streetaddress{P.O. Box 1212}
  \city{Manila, Philippines}
  %\state{Ohio}
  %\postcode{43017-6221}
}
\email{redacted}

\author{redacted}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{redacted}
  %\streetaddress{P.O. Box 1212}
  \city{Manila, Philippines}
  %\state{Ohio}
  %\postcode{43017-6221}
}
\email{redacted}

\author{redacted}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{redacted}
  %\streetaddress{P.O. Box 1212}
  \city{Manila, Philippines}
  %\state{Ohio}
  %\postcode{43017-6221}
}
\email{redacted}

\author{redacted}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{redacted}
  %\streetaddress{P.O. Box 1212}
  \city{Manila, Philippines}
  %\state{Ohio}
  %\postcode{43017-6221}
}
\email{redacted}



% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{redacted}


\begin{abstract}
In a university setting, academic timetabling has been an open opportunity for developers and system designers. It is usually focused on generating schedules, managing conflicts, accommodating constraints and even allocating respective logistical needs. There are several off-the-shelf and customized systems that have been developed to accommodate the varying needs of different universities and organizations. The usage and the underlying human factors when using these systems is another consideration that we can tackle with these enrollment systems. In this paper, we attempt to discover, design, implement an academic course scheduling system that considers user collaboration with other humans and with the computer itself. We iterated on developing a prototype for course scheduling, assigning of faculty and other pre-enrollment tasks. We observed stakeholders such as Department Chair, Academic Officers and other key personnel and inquired into their pains and struggles in academic course loading systems. To help them in this process, we present ASSYSTX: An online platform that supports collaboration between key personnel involved in enrollment systems. We also identified key collaboration points towards providing affordances that cater to the needs of these personnel. 
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10003120.10003130.10011762</concept_id>
       <concept_desc>Human-centered computing~Empirical studies in collaborative and social computing</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10002951.10003227.10003233</concept_id>
       <concept_desc>Information systems~Collaborative and social computing systems and tools</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Empirical studies in collaborative and social computing}
\ccsdesc[300]{Information systems~Collaborative and social computing systems and tools}


\keywords{Course Enrollment, Faculty Loading, Collaboration}


\maketitle

\input{samplebody-conf}

\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
